---
title: "Trump Inauguration Contributions"
resource_files:
- .httr-oauth
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme: cerulean

---

```{r setup, include=FALSE}

library(flexdashboard)
library(tidyverse)
library(lubridate)
library(janitor)
library(glue)
library(plotly)
library(DT)
library(googlesheets)
library(kableExtra)
library(leaflet)
# library(ggmap)
library(RColorBrewer)
library(htmlwidgets)
library(htmltools)
library(tigris)
options(tigris_class = "sf")


#load data from rds file created in step 01
contribs <- readRDS("contribs_saved.rds")


```





Donors to 2017 Inauguration 
=====================================
To filter, click on the boxes at the top of the columns. To sort, use the up/down arrows by the column names. (Click [here](https://www.dropbox.com/s/249a7wvb4goj0rn/fec_doc_trump_inaug_1.pdf?dl=1) for original FEC pdf document.) 

Row 
-----------------------------------------------------------------------

```{r}

contribs_inaug_only <- contribs %>% 
  select(
    individual_or_organization,
    contributor_name,
    org_name,
    parent_company,
    city,
    state,
    total_amount = inaug_2017_total
  ) %>% 
  mutate(
    individual_or_organization = as.factor(str_to_upper(individual_or_organization)),
    org_name = str_to_upper(org_name),
    parent_company = str_to_upper(parent_company)
  ) %>% 
  arrange(individual_or_organization, desc(total_amount))


datatable(contribs_inaug_only,
          rownames = FALSE,
          filter = "top",
          extensions = 'Buttons', 
          options = list(searchHighlight = TRUE, bPaginate = FALSE, dom = 'Bfrtip',
       buttons = c('copy', 'csv', 'excel', 'print')
          )) %>% 
      formatCurrency('total_amount', digits = 0) %>% 
      formatStyle("total_amount", color = "darkgreen") %>% 
      formatStyle('contributor_name', fontWeight = 'bold') 
      # formatStyle("salary", color = "darkred") %>% 
    #   formatStyle(
    #   'inaug_2017_total',
    #   background = styleColorBar(contribs_table$inaug_2017_total, 'steelblue'),
    #   backgroundSize = '100% 90%',
    #   backgroundRepeat = 'no-repeat',
    #   backgroundPosition = 'center'
    # )


```

Row
-----------------------------------------------------------------------

### Box 1

```{r}
valueBox("15", icon = "fa-pencil")

```

### Box 2

```{r}
valueBox("15", icon = "fa-pencil")

```

### Box 3

```{r}
valueBox("15", icon = "fa-pencil")

```



Previous donor activities
=====================================
To filter, click on the boxes at the top of the columns. To sort, use the up/down arrows by the column names.

Row {data-height=1000}
-----------------------------------------------------------------------

```{r}



```


FEC original pdf file
=====================================
Click here to view the original pdf filing submitted to the FEC by the Trump inaugural committee. [I'm an inline-style link with title](https://www.google.com "Google's Homepage")